### 2014-10-31 fundamentals/impl.tex
fixed possesion

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total computer hours, using
the \Cyclus library via its resource exchange \gls{API}.
The HTC infrastructure has also been utilized to run and collect
information from full \Cyclus simulations running in parallel on $10^3$
machines reliably for order $10^5$ simulations.

@@

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities, so advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implemenets the
\Class{Trader} interface, and thus institutions and regions, can
adjust the resource flow preferences of their managed facilities, respectively. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
designed to handle hierarchies of arbitrary depth.
A simulation can proceed without regions and institutions (i.e.,  only facilities)
or with archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It straightforward
to implement agents that deploy copies of themselves or schedule their
own decommissioning.  Because regions, institutions, and facilities are all
agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atomic and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

>>>>

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange \gls{API}.
The HTC infrastructure has also been utilized to run and collect
information from full \Cyclus simulations running in parallel on $10^3$
machines reliably for order $10^5$ simulations.

@@

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities, so advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implemenets the
\Class{Trader} interface, and thus institutions and regions can
adjust the resource flow preferences of their managed facilities, respectively. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
designed to handle hierarchies of arbitrary depth.
A simulation can proceed without regions and institutions (i.e.,  only facilities)
or with archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It is straightforward
to implement agents that deploy copies of themselves or schedule their
own decommissioning.  Because regions, institutions, and facilities are all
agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.
